Generate data for multispecies modeling, including diet!

### 2020-10-06 NOBAmsdiets.Rmd
add survey names to saved file when reading in

# object in memory is no longer the same as saved files, need to read back into same configuration
# list of files in directory with surveyB.rds ending
# append to survObsBiom
survs <- list.files(path=d.name, pattern = "*surveyB.rds", full.names = TRUE)
survey.name <-  
survObsBiom <- lapply(survs, readRDS)

@@

# why is herring missing from both?
herring <- NOBAom_ms$truebio_ss %>%
  filter(species %in% c("Norwegian_ssh")) %>%
  group_by(species, time) %>%
  summarise(totB = sum(atoutput))

>>>>

# object in memory is no longer the same as saved files, need to read back into same configuration
# list of files in directory with surveyB.rds ending
# append to survObsBiom
# apply survey name from filename
survs <- list.files(path=d.name, pattern = "*surveyB.rds", full.names = TRUE)
survey.name <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s*surveyB.rds"))[,2]
survObsBiom <- lapply(survs, readRDS)
names(survObsBiom) <- survey.name

@@

# why is herring missing from both?
# herring <- NOBAom_ms$truebio_ss %>%
#   filter(species %in% c("Norwegian_ssh")) %>%
#   group_by(species, time) %>%
#   summarise(totB = sum(atoutput))
